\begin{thebibliography}{KEY99}
\bibitem[BML+90]{BML+90}
Byrn, R.A., J. Mordenti, C. Lucas, D. Smith, S.A. Marsters, J.S. Johnson, P. Cossum, S.M. Chamow, F.M. Wurm, T. Gregory and et al.
\newblock Biological properties of a CD4 immunoadhesin..
\newblock {\em Nature}, 344(6267):667-70, 1990.
\newblock 
\bibitem[CIF+99]{CIF+99}
Crosignani, A., P. Invernizzi, R. Ferrari, A. Manzin, S. Bruno, M. Zuin, F.B. Bianchi and M. Podda.
\newblock Exacerbation of chronic hepatitis D during interferon alpha administration..
\newblock {\em Ital J Gastroenterol Hepatol}, 31(1):66-9, 1999.
\newblock 
\bibitem[FBC+92]{FBC+92}
Fusconi, M., H. Baum, A. Caselli, F. Cassani, G. Ballardini, M. Lenzi, U. Volta, D. Zauli and F.B. Bianchi.
\newblock Demonstration of peptide-specific and cross-reactive epitopes in proteins reacting with antimitochondrial antibodies of primary biliary cirrhosis..
\newblock {\em J Hepatol}, 15(1-2):162-9, 1992.
\newblock 
\bibitem[Gob]{Gob}
Gobry, F.
\newblock cECI est un T\AA{}ST\'EO\'eO G\"unther.
\newblock 
\bibitem[KMH+99]{KMH+99}
Kerkar, N., Y. Ma, M. Hussain, L. Muratori, C. Targett, R. Williams, F.B. Bianchi, G. Mieli-Vergani and D. Vergani.
\newblock A novel assay for detecting antibodies to cytochrome P4502D6, the molecular target of liver kidney microsomal antibody type 1..
\newblock {\em J Immunol Methods}, 223(2):227-35, 1999.
\newblock 
\bibitem[LBS+99]{LBS+99}
Lenzi, M., S. Bellentani, G. Saccoccio, P. Muratori, F. Masutti, L. Muratori, F. Cassani, F.B. Bianchi and C. Tiribelli.
\newblock Prevalence of non-organ-specific autoantibodies and chronic liver disease in the general population: a nested case-control study of the Dionysos cohort [see comments].
\newblock {\em Gut}, 45(3):435-41, 1999.
\newblock 
\bibitem[MCM+98]{MCM+98}
Muratori, L., M. Cataleta, P. Muratori, M. Lenzi and F.B. Bianchi.
\newblock Liver/kidney microsomal antibody type 1 and liver cytosol antibody type 1 concentrations in type 2 autoimmune hepatitis..
\newblock {\em Gut}, 42(5):721-6, 1998.
\newblock 
\bibitem[VDF+98a]{VDF+98}
Volta, U., L. De Franceschi, F. Lari, N. Molinaro, M. Zoli and F.B. Bianchi.
\newblock Coeliac disease hidden by cryptogenic hypertransaminasaemia..
\newblock {\em Lancet}, 352(9121):26-9, 1998.
\newblock 
\bibitem[VDF+98b]{VDF+98b}
Volta, U., L. De Franceschi, N. Molinaro, F. Cassani, L. Muratori, M. Lenzi, F.B. Bianchi and A.J. Czaja.
\newblock Frequency and significance of anti-gliadin and anti-endomysial antibodies in autoimmune hepatitis..
\newblock {\em Dig Dis Sci}, 43(10):2190-5, 1998.
\newblock 
\bibitem[ZCB99]{ZCB99}
Zauli, D., F. Cassani and F.B. Bianchi.
\newblock Auto-antibodies in hepatitis C..
\newblock {\em Biomed Pharmacother}, 53(5-6):234-41, 1999.
\newblock 
\end{thebibliography}
