\begin{thebibliography}{KEY99}
\bibitem[Axelsen et al., 1995]{AKM95}
Axelsen, P. H., Kaufman, B. K., McElhaney, R. N. and Lewis, R. N. A. H.
\newblock The {I}nfrared {D}ichroism of {T}ransmembrane {H}elical {P}olypeptides.
\newblock {\em Biophysical Journal}, 69:2770-2781, 1995.
\newblock 
\bibitem[Droppa et al., 1999]{DKP+99}
Droppa, M., K\'ota, Z., P\'ali, T., Szalontai, B., Horv\'ath, L. I. and Horv\'ath, G.
\newblock {\em Structural-{F}unctional organization of thylakoids in developing chloroplasts}, 1999, pages 55-60.
\newblock Kluwer Academic Publishers, 1999.
\newblock 
\bibitem[Jackson and Mantsch, 1995]{JM95}
Jackson, M. and Mantsch, H. H.
\newblock The {U}se and {M}isuse of {FTIR} {S}pectroscopy in the {D}etermination of {P}rotein {S}tructure.
\newblock {\em Critical Reviews in Biochemistry and Molecular Biology}, 30(2):95-120, 1995.
\newblock 
\bibitem[K\'ota et al., 1999]{KSD+99}
K\'ota, Z., Szalontai, B., Droppa, M., Horv\'ath, G. and P\'ali, T.
\newblock Fourier transform infrared and electron paramagnetic resonance spectroscopic studies of thylakoid membranes.
\newblock {\em Journal of Molecular Structure}, 480-481(SI):395-400, 1999.
\newblock 
\bibitem[K\'ota et al., 2002]{Kota2002}
K\'ota, Z., Horv\'ath, L. I., Droppa, M., Horv\'ath, G., Farkas, T. and P\'ali, T.
\newblock Protein assembly and heat stability in developing thylakoid membranes during greening.
\newblock {\em PNAS}, 99(19):12149-12154, 2002.
\newblock 
\bibitem[Kamnev et al., 2001]{Kamnev01}
Kamnev, A. A., Tarantilis, P. A., Antonyuk, L. P., Bespalova, L. A., Polissiou, M. G., Colina, M., Gardiner, P. H. E. and Ignatov, V. V.
\newblock Fourier transform {R}aman spectroscopic characterisation of cells of the plant-associated soil bacterium {A}zospirillum brasilense {S}p7.
\newblock {\em Journal of Molecular Structure}, 536--564:199--207, 2001.
\newblock 
\bibitem[Lindahl et al., 1997]{LFW+97}
Lindahl, M., Funk, C., Webster, J., Bringsmark, S., Adamska, I. and Andersson, B.
\newblock Expression of {ELIP}s and {PS} {II}-{S} protein in spinach during acclimative reduction of the {P}hotosystem {II} antenna in response to increased light intensities.
\newblock {\em Photosynthesis Research}, 54:227-236, 1997.
\newblock 
\bibitem[Mantsch and McElhaney, 1991]{MM01}
Mantsch, H. H. and McElhaney, R. N.
\newblock Phospholipid phase transitions in model and biological membranes as studied by infrared spectroscopy.
\newblock {\em Chemistry and Physics of Lipids}, 57:213-226, 1991.
\newblock 
\bibitem[Marsh and Horv\'ath, 1998]{MH98}
Marsh, D. and Horv\'ath, L. I.
\newblock Structure, dynamics and composition of the lipid-protein interface. {P}erspectives from spin-labelling.
\newblock {\em Biochimica et Biophysica Acta}, 1376:267-296, 1998.
\newblock 
\bibitem[Marsh, 1999]{M99}
Marsh, D.
\newblock Interactions at the {M}embrane {S}urface {S}tudied by {S}pin {L}abel {ESR} {S}pectroscopy.
\newblock {\em Bioscience Reports}, 19(4):253-259, 1999.
\newblock 
\bibitem[Marsh, 2001a]{M01}
Marsh, D.
\newblock Polarity and permeation profiles in lipid membranes.
\newblock {\em PNAS}, 98(14):7777-7782, 2001.
\newblock 
\bibitem[Marsh, 2001b]{M01a}
Marsh, D.
\newblock Polarity and permeation profiles in lipid membranes. {P}art {II}..
\newblock {\em PNAS}, 98(14):7783-7785, 2001.
\newblock 
\bibitem[Smirnov et al., 1995]{Smirnov95}
Smirnov, A. I., Smirnova, T. I. and Morse, P. D.
\newblock Very {H}igh {F}requency {E}lectron {P}aramagnetic {R}esonance of 2,2,6,6- {T}etramethyl-1-{P}iperidinyloxy in 1,2-{D}ipalmitoyl-sn-{G}lycero-3-{P}hosphatidylcholine {L}iposomes: {P}artitioning and {M}olecular {D}ynamics.
\newblock {\em Biophysical Journal}, 68(6):2350-2360, 1995.
\newblock 
\end{thebibliography}
